---
title: "Homework 1"
author: Yifan Su
due date: 9/19/2020
output: github_document
---

This is the solution to Homework 1.

```{r message=FALSE}
library(tidyverse)
```

## Problem 1

#### First code chunk

Create a data frame comprised of a random sample, a logicla vector, a character vector, and a factor vector.

```{r message=FALSE}
prob1_df = 
  tibble(
    samp = rnorm(n = 10),
    samp_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    fac_vec = factor(c("L", "L", "M", "S", "M", "S", "L", "M", "L", "M"))
  )
```

 Take the mean of each variables.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fac_vec))
```

I can get the mean of sample and the logical vector, but not for that of the other two. 

```{r eval=FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fac_vec))
```

I can get numeric result of all variables except for the character vector. Although it is unusuall, I can get numeric result of the factor vector.

#### Second code chunk

Convert logical vector to different factors.

```{r}
as.numeric(pull(prob1_df, samp_0)) * pull(prob1_df, samp)
factor(pull(prob1_df, samp_0)) * pull(prob1_df, samp)
as.numeric(factor(pull(prob1_df, samp_0))) * pull(prob1_df, samp)
```


## Problem 2

Download "penguins" dataset and load it.

```{r}
data("penguins", package = "palmerpenguins")
ls(penguins)
nrow(penguins)
ncol(penguins)
summary(pull(penguins, flipper_length_mm))[4]
```

The dataset "penguins" has 344 rows and 8 columns. 

Variables in it include bill_length_mm,flipper_length_mm, sex and year, etc. 

The mean flipper length is `r summary(pull(penguins, flipper_length_mm))[4]`.

```{r}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species))
```

Then, we get a scatterplot about bill and flipper length.